A search for intermediate-mass black holes mergers in the \\second LIGO--Virgo observing run with the Bayes Coherence Ratio

### 2021-07-06 main.tex
update tables

\documentclass[%
%reprint,
%superscriptaddress,
%groupedaddress,
%unsortedaddress,
%runinaddress,
%frontmatterverbose, 
% preprint,
%preprintnumbers,
 nofootinbib,
%nobibnotes,
%bibnotes,
 amsmath,amssymb,
 aps,
%pra,
%prb,
%rmp,
%prstab,
%prstper,
%floatfix,
 twocolumn,
 superscriptaddress
]{revtex4-2}

\usepackage{aas_macros}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{array}
\usepackage{color,units}
\usepackage[dvipsnames]{xcolor} % for more colours!
\usepackage{lineno}
\usepackage{dcolumn}
\usepackage{longtable}
\usepackage[normalem]{ulem} %% for striking out text
\usepackage{subfigure}
\usepackage[T1]{fontenc}
\usepackage[breaklinks]{hyperref}
\usepackage{booktabs}
\usepackage{xspace} 
\usepackage{bm}% bold math
\usepackage{graphicx} % Include figure files
% \usepackage{authblk}

@@

% Keywords
\newcommand{\bilby}{{\sc \href{https://lscsoft.docs.ligo.org/bilby/}{\texttt{Bilby}}}\xspace}
\newcommand{\bilbypipe}{{\sc \texttt{bilby\_pipe}}\xspace}
\newcommand{\dynesty}{{\sc \texttt{dynesty}}\xspace}
\newcommand{\cpnest}{{\sc cpnest}\xspace}
\newcommand{\ptemcee}{{\sc ptemcee}\xspace}
\newcommand{\gwpy}{{\sc \href{https://gwpy.github.io/}{\texttt{GWpy}}}\xspace}

\newcommand{\imrphenomp}{{\sc \texttt{IMRPhenomPv2}}\xspace}
\newcommand{\seob}{{\sc \texttt{SEOBNRv4PHM}}\xspace}
\newcommand{\nrsur}{{\sc \texttt{NRSur7dq4}}\xspace}
\newcommand{\imrxhm}{{\sc \texttt{IMRPhenomXPHM}}\xspace}

\newcommand{\gstlal}{{\sc GstLAL}\xspace}
\newcommand{\cwb}{{\sc cWB}\xspace}
\newcommand{\spiir}{{\sc SPIIR}\xspace}
\newcommand{\mbta}{{\sc MBTAOnline}\xspace}
\newcommand{\pycbc}{{\sc \href{https://pycbc.org/}{{PyCBC}}}\xspace}

\newcommand{\GWTC}{{\sc \href{https://ui.adsabs.harvard.edu/abs/2019PhRvX...9c1040A/abstract}{{GWTC-1}}}\xspace}
\newcommand{\OGC}{{\sc \href{https://ui.adsabs.harvard.edu/abs/2020ApJ...891..123N/abstract}{{2-OGC}}}\xspace}
\newcommand{\IAS}{{\sc \href{https://ui.adsabs.harvard.edu/abs/2020PhRvD.101h3030V/abstract}{{IAS}}}\xspace}

% math keywords 
\newcommand{\fancytext}[1]{{\relax\ifmmode#1\else $#1$\fi}\xspace}
\newcommand{\mathcmd}[1]{{\sc \relax\ifmmode#1\else $#1$\fi}\xspace}
\newcommand{\bcr}{\mathcmd{\rho_\text{BCR}}}
\newcommand{\bgrdbcr}{\mathcmd{\rho_\text{BCR}^\textit{b}}}
\newcommand{\candbcr}{\mathcmd{\rho_\text{BCR}^\textit{c}}}

\newcommand{\bcrodds}{\mathcmd{\mathcal{O}_{\mathrm{BCR}}}}
\newcommand{\pycbcstat}{\mathcmd{\rho_\text{PC}}}
\newcommand{\snr}{\mathcmd{\rho}}
\newcommand{\psd}{\mathcmd{P(f)}}
\newcommand{\msun}{\mathcmd{\text{M}_\odot}}
\newcommand{\mtot}{\mathcmd{M}}
\newcommand{\parameters}{\mathcmd{\vec{\theta}}}
\newcommand{\prior}{\mathcmd{\pi(\parameters)}}
\newcommand{\template}{\mathcmd{\mu(\parameters)}}
\newcommand{\fap}{\mathcmd{p_N}}

\newcommand{\pastro}{\fancytext{p_\text{astro}}}
\newcommand{\pastrobcr}{\fancytext{p_\text{S}}}
\newcommand{\untunedpastrobcr}{\fancytext{p_\text{S}^{\prime}}}
\newcommand{\pastroext}{\fancytext{p_\text{astro}^{\text{ext}}}}
\newcommand{\pval}{\fancytext{\text{p-value}}}
% Table settings
\renewcommand{\aboverulesep}{0pt}
\renewcommand{\belowrulesep}{0pt}
% \setlength\cellspacetoplimit{2pt}
% \setlength\cellspacebottomlimit{2pt}

\newcolumntype{C}{>{\centering\arraybackslash}X}
\newcolumntype{L}{>{\arraybackslash}X}

% Aesthetic colours
\definecolor{dodgerblue}{HTML}{1E90FF}
\definecolor{viennared}{HTML}{DA0A14}
\definecolor{ctorange}{HTML}{FF6C0C}
\definecolor{wales}{HTML}{ff0038}
\definecolor{benettongreen}{HTML}{009421}
\definecolor{valenciacfred}{HTML}{ee3524}
\definecolor{barcelonafcgold}{HTML}{edbb00}
\definecolor{jam}{HTML}{A50B5E}
\definecolor{austriawien}{HTML}{441678}
\definecolor{italia90green}{HTML}{009966}
\definecolor{ferrarired}{HTML}{ff2800}
\definecolor{gray}{HTML}{F0F0F0}
\definecolor{LightCyan}{rgb}{0.88,1,1}
\newcolumntype{a}{>{\columncolor{gray}}c}
\newcolumntype{b}{>{\columncolor{white}}c}

@@

\begin{abstract}
The detection of an intermediate-mass black hole population ($10^2-10^6$~\msun) will provide clues to their formation environments (e.g., disks of active galactic nuclei, globular clusters) and illuminate a potential pathway to produce supermassive black holes. Ground-based gravitational-wave detectors are in principle sensitive to such mergers and have been used to detect one $142^{+28}_{-16}\ \msun$ intermediate-mass black hole formation event. Ground-based detector data contain numerous short-duration noise transients that can mimic the gravitational-wave signals from merging intermediate-mass black holes, limiting the sensitivity of searches. Here we demonstrate a Bayesian-inspired ranking statistic to detect binary black hole mergers with a total mass $\gtrsim55$~\msun. We use this statistic to identify candidate events with total masses $>55$~\msun using data from LIGO's second observing run. Our analysis does not yield evidence for new intermediate-mass black holes. However, we find support for some stellar-mass binary black holes not reported in the first LIGO--Virgo gravitational-wave transient catalog, GWTC-1.
\end{abstract}

@@

A variety of techniques have been employed to search for $10^{4} - 10^{6}\ \msun$ intermediate-mass candidates including reverberation mapping~\cite{Peterson:2014:SSRv}, direct kinematic measurements~\cite{Schodel:2002:Natur, Kiziltan:2017:Natur}, applying macroscopic galaxy to black hole mass scaling relations ($M_{BH}$-$\sigma$ and $M_{BH}$-L relations)~\cite{Graham:2013:ApJ, Wevers:2017:MNRAS}, studying  X-ray luminosity and spectra~\cite{Greene:2004:ApJ, Lin:2020:ApJL}, gravitational lensing of gamma-ray burst light curves~\cite{paynter_evidence_2021}, and others~\cite{Greene:2020:ARA&A, Koliopanos:2017:mbhe, Mezcua:2017:IJMPD}). However, because intermediate-mass black holes have smaller gravitational spheres of influence than those of supermassive black holes, it is much more challenging to observe them with these observational techniques~\cite{Mezcua:2017:IJMPD}. Additionally, the numerous intermediate-mass black hole candidates discovered using these techniques are ambiguous as other sources can describe observations from the candidates (e.g., light sources orbiting clusters of stellar-mass black holes~\cite{Ridolfi:2016:MNRAS, Freire:2017:MNRAS}, anisotropic emission from neutron stars~\cite{Israel:2017:MNRAS, RodriguezCastillo:2020:ApJ}).

Stellar mass ($M_\text{BH} < 10^{2} \ \msun$) and supermassive black holes ($M_\text{BH} > 10^{6} \ \msun$) have been observed and well studied since the 1970s~\cite{Webster:1972:Natur, Balick:1974:ApJ, Ghez:1998:ApJ, Genzel:2010:RvMP, Abbott:2019:PhRvX, EventHorizonTelescopeCollaboration:2019:ApJL, Abbott:2020:arXiv}. However, there is a deficiency of observational evidence for black holes in the intermediate-mass range $10^{2} - 10^{6}\ \msun$. The discovery of an intermediate-mass black hole population will bridge this observational gap, probe intermediate-mass formation environments (e.g. accretion disks of active galactic nuclei~\cite{Tagawa:2021:ApJ, Li:2021:arXiv, Samsing:2020:arXiv, Tagawa:2020:ApJ, Ishibashi:2020:A&A, Grobner:2020:A&A, Yang:2019:PhRvL, McKernan:2019:ApJL, Yang:2019:ApJ, McKernan:2018:ApJ, Bellovary:2016:ApJL, McKernan:2014:MNRAS, McKernan:2012:MNRAS}, the centers of dense stellar clusters~\cite{Banerjee:2021:MNRASa, Zevin:2021:ApJ,Mapelli:2021:arXiv,Weatherford:2021:ApJL, Bouffanais:2021:arXiv, Ballone:2021:MNRAS, Kumamoto:2021:arXiv, Banerjee:2021:MNRASb, Martinez:2020:ApJ, Romero-Shaw:2020:ApJL, Anagnostou:2020:PASA}, Population-III stars~\cite{Toubiana:2021:PhRvL, Farrell:2021:MNRAS, Safarzadeh:2020:ApJL, Liu:2020:MNRAS, Inayoshi:2017:MNRAS}), and illuminate our understanding of supermassive black hole formation~\cite{Askar:2021:MNRAS, ArcaSedda:2019:arXiv, Amaro-Seoane:2007:CQGra, Gurkan:2006:ApJL}.

Compact binary coalescences (CBCs) can provide unambiguous gravitational-wave signals for intermediate-mass candidates e.g., the $142^{+28}_{-16}\ \msun$ remnant observed from the gravitational-wave event GW190521~\cite{Abbott:2020:PhRvL} and other candidates~\cite{ligo_imbh_search, ligo_imbh_o3, pycbc_imbh}. As a binary's total mass $\text{M}_{T}$ is associated with its gravitational-wave merger frequency, $f\sim \text{M}_{T}^{-1}$,  ground-based gravitational-wave detectors ($f\sim 10^1 - 10^3\ \text{Hz}$) are sensitive to the last milliseconds of merging systems with $100 \msun < \text{M}_{T} < 400 \msun$~\cite{LIGOScientificCollaboration:2015:CQGra, Martynov:2016:PhRvD, Moore_2014}, while space-based detectors ($f \sim 10^{-2} - 10^1\ \text{Hz}$) can study the full signals of merging systems with $10^4 \msun < \text{M}_{T} < 10^7 \msun$~\cite{ Moore_2014, Lu:2019:PhRvD}. Because of the short-duration of intermediate-mass gravitational-wave signals in ground-based detectors, data quality is critical for their detection. Gravitational-wave data is characterized by numerous non-stationary terrestrial artifacts called \textit{glitches}~\cite{ pycbc_short_duration_transients, pe_with_glitch, blip_glitches}. Like signals from intermediate mass mergers, most glitches last for a fraction of a second, making them difficult to distinguish from astrophysical signals. These glitches can decrease the sensitivity of searches for binary black hole mergers with total masses $>55$~\msun ~\cite{pycbc_short_duration_transients}.

Although a significant fraction of the glitches can be identified by testing them for coherence amongst two or more detectors and performing matched-filtering, these methods are insufficient to identify all glitches~\cite{ pycbc_short_duration_transients, pe_with_glitch, blip_glitches}. One method to discriminate more glitches while searching for CBC is the Bayesian odds~\cite{bci, kanner2016leveraging, BCR1, BCR2, bcr_gw151216, bayesian_odds}. The Bayesian Coherence Ratio \bcr~\cite{BCR1,BCR2} is a Bayesian odds comparing the probability that the data contains coherent signals vs. incoherent glitches. In this paper, we the \bcr to rank O2's candidate gravitational-wave signals from $55-500\ \msun$ (detector-frame) total mass systems. For each candidate, we calculate the probability of astrophysical origin, \pastrobcr and compare to candidate events reported by other authors including the LIGO-Virgo-KAGRA (LVK) collaboration in \GWTC~\cite{GWTC1}, the \pycbc-team~\cite{pycbc_code, pycbc_og0, pycbc_og1, pycbc_og2, pycbc_og3, pycbc_og4, pycbc_og5, pycbc_og6, pycbc_single_det, pycbc_ogc_2}, by the Institute of Advanced study's team (\IAS)~\cite{IAS0, IAS1, IAS2}, or by \citet{bayesian_odds}.

We find that (a) high-mass events reported in the \GWTC, including GW170729 (the heaviest event in \GWTC) are very statistically significant $\pastrobcr>0.9$; (b) three out of the eight \IAS events and candidates have $\pastrobcr>0.5$, corroborating \IAS's detection claims for GW170304, GW170727, and GW170817A; and that (c) our ranking statistic does not identify any new intermediate-mass black holes, but does identify an unreported marginal stellar-mass binary black hole candidate, 170222 with $\pastrobcr\sim0.5$. %\avi{Need to doublecheck that this wasn't in the PyCBC sub-threshold paper}.

@@

Bayesian inference offers an alternative means to rank the significance of candidate events by computing the odds that the data contain a transient gravitational-wave signal versus instrumental glitches~\cite{BCR1}. This method relies on accurate models for the signal and glitch morphologies~\cite{BCR1}. In principle, Bayesian odds is the optimal method for hypothesis testing~\cite{BCR2}. Much of its power comes from the Bayesian evidence, the likelihood of the data given a hypothesis. However, the evidence is not used in current matched filter searches. Here, we explore a hybrid frequentist/Bayesian ranking statistic that makes use of the Bayesian evidence. We compute the Bayesian evidence under the assumption that they either contain a coherent gravitational-wave signal, noise, or a glitch ($Z^S, Z^N, Z^G$, defined in Appendix~\ref{sec:bayesianEvidEval}). However, instead of computing true Bayesian odds, we use the evidences as a ranking statistic. We form a bootstrapped distribution of the evidence for simulated foreground and background events in order to form a frequentist ranking statistic.

@@

We acquire O2 candidate signal triggers (times when the detector's data has a signal-to-noise ratio above a predetermined threshold) for \bcr analysis from \pycbc~\cite{pycbc_code, pycbc_og0, pycbc_og1, pycbc_og2, pycbc_og3, pycbc_og4, pycbc_og5, pycbc_og6}.  Some of the triggers are associated with gravitational-wave events and candidates, while others are glitches. We also acquire background and simulated triggers from \pycbc to calculate \bgrdbcr and estimate values for $\{\hat{\pi}^S,\hat{\pi}^G\}$ (see Appendix~\ref{apdx:tuning-prior-odds} for details on the estimation process). Note that the triggers are divided into two week time-frames because the detector's sensitivity does not stay constant throughout the eight-month-long observing period~\cite{pycbc_og4}.

\begin{table}[t]
\caption[BBH parameters correspond to duration $<454\ \text{ms}$]{\label{tab:parameters}Trigger-selection parameter space (parameters correspond to signals with durations $<454 \ \text{ms}$). }
\centering
\begin{tabular}{lrr}
\toprule
  & Minimum & Maximum\\
\midrule
Component Mass 1 [\msun] & 31.54 & 491.68\\
Component Mass 2 [\msun] & 1.32 & 121.01\\
Total Mass [\msun] & 56.93 & 496.72\\
Chirp Mass [\msun] & 8.00 & 174.56\\
Mass Ratio & 0.01 & 0.98\\
\end{tabular}
\end{table}

For our study, we filter triggers to include those in the parameter ranges presented in Table~\ref{tab:parameters}. This region focuses our analysis on binary black hole mergers with total masses above $> 55 \msun$, corresponding to binary systems with signal durations $<454 \ \text{ms}$. The filtering process leaves us with $60,996$ background, $5,146$ simulated, and $25$ candidate signal triggers. We also include events and candidate events reported by \GWTC and the \IAS group in our list of candidate signal triggers.  A plot of the \pycbc triggers from April 23 - May 8, 2017, is presented in Fig.~\ref{fig:templateBank}. This figure also depicts the gravitational-wave templates used by \pycbc's search.

\begin{figure*}[!ht]
{\centering \includegraphics[width=0.75\linewidth]{images/template_bank.png}
}
% time for chunk 14
% 1176955218, Apr 23, 2017, 4:00 UTC
% 1178294418, May 08, 2017, 16:00 UTC
\caption[ BCR search space.]{The templates (pink) used by \pycbc to search a section of O2 data from $\text{April 23 - May 8, 2017}$. Our search is constrained to the parameter space enclosed by the dashed line. The candidate, background, and simulated triggers detected in this region of the parameter space during this period are plotted in orange, gray, and blue, respectively.}\label{fig:templateBank}
\end{figure*}

@@

Finally, with the \candbcr and \bgrdbcr, we calculate the candidate signal's \pastrobcr. We present the \pastrobcr with \pastro of other pipelines for comparison in Table~\ref{tab:results}.

@@

Various pipeline \pastro are not mathematically equivalent~\cite{Galaudage:2020:PhRvD}. However, by comparing pipeline \pastro values for a given candidate along with \pastrobcr in Table~\ref{tab:results}, we can compare how significant each pipeline deems various candidates. Note that the $\hat{\pi}^S$ and $\hat{\pi}^G$ values utilized for each time-frame are reported in Appendix~\ref{apdx:alphabeta}.

@@

\bibliography{high_mass_bib}% Produces the bibliography via BibTeX.

\end{document}
%
% ****** End of file apssamp.tex ******

>>>>

\documentclass[
% preprint,
%preprintnumbers,
 nofootinbib,
 amsmath,amssymb,
 aps,
 twocolumn,
 superscriptaddress
]{revtex4-2}

\usepackage{aas_macros}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{array}
\usepackage{units}
\usepackage{xcolor} % for more colours!
\usepackage{lineno}
\usepackage{dcolumn}
\usepackage[normalem]{ulem} %% for striking out text
\usepackage{subfigure}
\usepackage[T1]{fontenc}
\usepackage[breaklinks]{hyperref}
\usepackage{xspace} 
\usepackage{bm}% bold math
\usepackage{graphicx} % Include figure files

%%% Table stuff
\usepackage{longtable}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{colortbl}

\usepackage{nicematrix}

@@

% Keywords
\newcommand{\bilby}{{\sc \href{https://lscsoft.docs.ligo.org/bilby/}{\texttt{Bilby}}}\xspace}
\newcommand{\bilbypipe}{{\sc \texttt{bilby\_pipe}}\xspace}
\newcommand{\dynesty}{{\sc \texttt{dynesty}}\xspace}
\newcommand{\cpnest}{{\sc cpnest}\xspace}
\newcommand{\ptemcee}{{\sc ptemcee}\xspace}
\newcommand{\gwpy}{{\sc \href{https://gwpy.github.io/}{\texttt{GWpy}}}\xspace}
\newcommand{\imrphenomp}{{\sc \texttt{IMRPhenomPv2}}\xspace}
\newcommand{\seob}{{\sc \texttt{SEOBNRv4PHM}}\xspace}
\newcommand{\nrsur}{{\sc \texttt{NRSur7dq4}}\xspace}
\newcommand{\imrxhm}{{\sc \texttt{IMRPhenomXPHM}}\xspace}
\newcommand{\gstlal}{{\sc GstLAL}\xspace}
\newcommand{\cwb}{{\sc cWB}\xspace}
\newcommand{\spiir}{{\sc SPIIR}\xspace}
\newcommand{\mbta}{{\sc MBTAOnline}\xspace}
\newcommand{\pycbc}{{\sc \href{https://pycbc.org/}{{PyCBC}}}\xspace}
\newcommand{\GWTC}{{\sc \href{https://ui.adsabs.harvard.edu/abs/2019PhRvX...9c1040A/abstract}{{GWTC-1}}}\xspace}
\newcommand{\OGC}{{\sc \href{https://ui.adsabs.harvard.edu/abs/2020ApJ...891..123N/abstract}{{2-OGC}}}\xspace}
\newcommand{\IAS}{{\sc \href{https://ui.adsabs.harvard.edu/abs/2020PhRvD.101h3030V/abstract}{{IAS}}}\xspace}

% math keywords 
\newcommand{\fancytext}[1]{{\relax\ifmmode#1\else $#1$\fi}\xspace}
\newcommand{\mathcmd}[1]{{\sc \relax\ifmmode#1\else $#1$\fi}\xspace}
\newcommand{\bcr}{\mathcmd{\rho_\text{BCR}}}
\newcommand{\bgrdbcr}{\mathcmd{\rho_\text{BCR}^\textit{b}}}
\newcommand{\candbcr}{\mathcmd{\rho_\text{BCR}^\textit{c}}}
\newcommand{\bcrodds}{\mathcmd{\mathcal{O}_{\mathrm{BCR}}}}
\newcommand{\pycbcstat}{\mathcmd{\rho_\text{PC}}}
\newcommand{\snr}{\mathcmd{\rho}}
\newcommand{\psd}{\mathcmd{P(f)}}
\newcommand{\msun}{\mathcmd{M_\odot}}
\newcommand{\mtot}{\mathcmd{M}}
\newcommand{\parameters}{\mathcmd{\vec{\theta}}}
\newcommand{\prior}{\mathcmd{\pi(\parameters)}}
\newcommand{\template}{\mathcmd{\mu(\parameters)}}
\newcommand{\fap}{\mathcmd{p_N}}
\newcommand{\totMlab}{\mathcmd{M_T^{\rm{lab}}}}
\newcommand{\pastro}{\fancytext{p_\text{astro}}}
\newcommand{\pastrobcr}{\fancytext{p_\text{S}}}
\newcommand{\untunedpastrobcr}{\fancytext{p_\text{S}^{\prime}}}
\newcommand{\tunedpastrobcr}{\fancytext{p_\text{S}}}
\newcommand{\pastroext}{\fancytext{p_\text{astro}^{\text{ext}}}}
\newcommand{\pval}{\fancytext{\text{p-value}}}

\newcommand{\pastroGwtcPycbc}{\fancytext{p_\text{astro}^{\text{pyCBC}}}}
\newcommand{\pastroGwtcGstlal}{\fancytext{p_\text{astro}^{\text{GstLAL}}}}
\newcommand{\pastroIas}{\fancytext{p_\text{astro}^{\text{IAS}}}}
\newcommand{\pastroPrat}{\fancytext{P(S|\text{d})}}
\newcommand{\pastroSing}{\fancytext{p_\text{astro}^{\text{S}}}}
\newcommand{\pastroOgcTwo}{\fancytext{p_\text{astro}^{\text{OGC2}}}}
\newcommand{\pastroOgcThree}{\fancytext{p_\text{astro}^{\text{OGC3}}}}
\newcommand{\tc}{\fancytext{t_c}}

% Table settings
\renewcommand{\aboverulesep}{0pt}
\renewcommand{\belowrulesep}{0pt}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\newcolumntype{L}{>{\arraybackslash}X}
\newcolumntype{a}{>{\columncolor{gray}}c}
\addtolength{\extrarowheight}{\belowrulesep}

@@

\begin{abstract}
The detection of an intermediate-mass black hole population ($10^2-10^6$~\msun) will provide clues to their formation environments (e.g., disks of active galactic nuclei, globular clusters) and illuminate a potential pathway to produce supermassive black holes. Ground-based gravitational-wave detectors are in principle sensitive to a subset of such mergers mergers and have been used to detect one $142^{+28}_{-16}~\msun$ intermediate-mass black hole formation event. Ground-based detector data contain numerous short duration noise transients that can mimic the gravitational-wave signals from merging intermediate-mass black holes, limiting the sensitivity of searches. Here we demonstrate a Bayesian-inspired ranking statistic to detect binary black hole mergers with a lab-frame total mass $\gtrsim55$~\msun. We use this statistic to identify candidate events with lab-frame total masses $\gtrsim55$~\msun using data from LIGO's second observing run. Our analysis does not yield evidence for new intermediate-mass black holes. However, we find support for some stellar-mass binary black holes not reported in the first LIGO--Virgo gravitational-wave transient catalog, GWTC-1.
\end{abstract}

@@

A variety of techniques have been employed to search for $10^{4} - 10^{6}~\msun$ intermediate-mass black hole (IMBH) candidates including reverberation mapping~\cite{Peterson:2014:SSRv}, direct kinematic measurements~\cite{Schodel:2002:Natur, Kiziltan:2017:Natur}, applying macroscopic galaxy to black hole mass scaling relations ($M_{BH}$-$\sigma$ and $M_{BH}$-L relations)~\cite{Graham:2013:ApJ, Wevers:2017:MNRAS}, studying  X-ray luminosity and spectra~\cite{Greene:2004:ApJ, Lin:2020:ApJL}, gravitational lensing of gamma-ray burst light curves~\cite{paynter_evidence_2021}, and others~\cite{Greene:2020:ARA&A, Koliopanos:2017:mbhe, Mezcua:2017:IJMPD}). However, because IMBH have smaller gravitational spheres of influence than those of supermassive black holes, it is much more challenging to observe them with these observational techniques~\cite{Mezcua:2017:IJMPD}. Additionally, the numerous IMBH candidates discovered using these techniques are ambiguous as other sources can describe observations from the candidates (e.g., light sources orbiting clusters of stellar-mass black holes~\cite{Ridolfi:2016:MNRAS, Freire:2017:MNRAS}, anisotropic emission from neutron stars~\cite{Israel:2017:MNRAS, RodriguezCastillo:2020:ApJ}).

Stellar mass ($M_\text{BH} < 10^{2}~\msun$) and supermassive black holes ($M_\text{BH} > 10^{6}~\msun$) have been observed and well studied since the 1970s~\cite{Webster:1972:Natur, Balick:1974:ApJ, Ghez:1998:ApJ, Genzel:2010:RvMP, Abbott:2019:PhRvX, EventHorizonTelescopeCollaboration:2019:ApJL, Abbott:2020:arXiv}. However, there is a deficiency of observational evidence for black holes in the intermediate-mass range $10^{2} - 10^{6}~\msun$. The discovery of an IMBH population will bridge this observational gap, probe IMBH formation environments (e.g. accretion disks of active galactic nuclei~\cite{Tagawa:2021:ApJ, Li:2021:arXiv, Samsing:2020:arXiv, Tagawa:2020:ApJ, Ishibashi:2020:A&A, Grobner:2020:A&A, Yang:2019:PhRvL, McKernan:2019:ApJL, Yang:2019:ApJ, McKernan:2018:ApJ, Bellovary:2016:ApJL, McKernan:2014:MNRAS, McKernan:2012:MNRAS}, the centers of dense stellar clusters~\cite{Banerjee:2021:MNRASa, Zevin:2021:ApJ,Mapelli:2021:arXiv,Weatherford:2021:ApJL, Bouffanais:2021:arXiv, Ballone:2021:MNRAS, Kumamoto:2021:arXiv, Banerjee:2021:MNRASb, Martinez:2020:ApJ, Romero-Shaw:2020:ApJL, Anagnostou:2020:PASA}, Population-III stars~\cite{Toubiana:2021:PhRvL, Farrell:2021:MNRAS, Safarzadeh:2020:ApJL, Liu:2020:MNRAS, Inayoshi:2017:MNRAS}), and illuminate our understanding of supermassive black hole formation~\cite{Askar:2021:MNRAS, ArcaSedda:2019:arXiv, Amaro-Seoane:2007:CQGra, Gurkan:2006:ApJL}.

Compact binary coalescences (CBCs) can provide unambiguous gravitational-wave signals for IMBH candidates e.g., the $142^{+28}_{-16}~\msun$ ($90\%$ credible intervals) remnant observed from the gravitational-wave event GW190521~\cite{Abbott:2020:PhRvL} and other candidates~\cite{ligo_imbh_search, ligo_imbh_o3, pycbc_imbh}. As a binary's total mass $\text{M}_{T}$ is associated with its gravitational-wave merger frequency, $f\sim \text{M}_{T}^{-1}$,  ground-based gravitational-wave detectors ($f\sim 10^1 - 10^3\ \text{Hz}$) are sensitive to the last milliseconds of merging systems with $100~\msun < \totMlab < 400~\msun$~\cite{LIGOScientificCollaboration:2015:CQGra, Martynov:2016:PhRvD, Moore_2014, Acernese:2015:CQGra}, while space-based detectors ($f \sim 10^{-2} - 10^1\ \text{Hz}$) can study the full signals of merging systems with $10^4~\msun < \totMlab < 10^7~\msun$~\cite{ Moore_2014, Lu:2019:PhRvD}. Because of the short duration of IMBH gravitational-wave signals in ground-based detectors, data quality is critical for their detection. Gravitational-wave data is characterized by numerous non-stationary terrestrial artifacts called \textit{glitches}~\cite{ pycbc_short_duration_transients, pe_with_glitch, blip_glitches}. Like signals from IMBH mergers, most glitches last for a fraction of a second, making them difficult to distinguish from astrophysical signals. These glitches can decrease the sensitivity of searches for binary black hole mergers with $\totMlab\gtrsim55$~\msun ~\cite{pycbc_short_duration_transients}.

Although a significant fraction of the glitches can be identified by testing them for coherence amongst two or more detectors and performing matched-filtering, these methods are insufficient to identify all glitches~\cite{ pycbc_short_duration_transients, pe_with_glitch, blip_glitches}. One method to discriminate more glitches while searching for CBCs is the Bayesian odds~\cite{bci, kanner2016leveraging, BCR1, BCR2, bcr_gw151216, bayesian_odds}. The Bayesian Coherence Ratio \bcr~\cite{BCR1,BCR2} is a Bayesian odds comparing the probability that the data contains coherent signals vs. incoherent glitches. In this paper, we use the \bcr to rank O2's candidate gravitational-wave signals from $55-500~\msun$ lab-frame total mass systems. For each candidate, we calculate the probability of astrophysical origin, \pastrobcr and compare to candidate events reported by the LIGO-Virgo-KAGRA (LVK) collaboration in \GWTC~\cite{GWTC1}, the \pycbc-team~\cite{pycbc_code, pycbc_og0, pycbc_og1, pycbc_og2, pycbc_og3, pycbc_og4, pycbc_og5, pycbc_og6, pycbc_single_det, pycbc_ogc_2}, by the Institute of Advanced study's team (\IAS)~\cite{IAS0, IAS1, IAS2}, or by \citet{bayesian_odds}.

We find that (a) events reported in \GWTC, including GW170729 (likely the most massive BBH system in \GWTC) are statistically significant $\pastrobcr>0.9$; (b) three out of the eight \IAS events and candidates have $\pastrobcr>0.5$, corroborating \IAS's detection claims for GW170304, GW170727, and GW170817A; and that (c) our ranking statistic does not identify any new IMBH, but does identify an unreported marginal stellar-mass binary black hole candidate, 170222 with $\pastrobcr\sim0.5$.

@@

Bayesian inference offers an alternative means to rank the significance of candidate events by computing the odds that the data contain a transient gravitational-wave signal versus instrumental glitches~\cite{BCR1}. This method relies on accurate models for the signal and glitch morphologies~\cite{BCR1}. In principle, Bayesian odds is the optimal method for hypothesis testing~\cite{BCR2}. Much of its power comes from the Bayesian evidence, the likelihood of the data given a hypothesis. However, the evidence is not used in current matched filter searches. Here, we explore a hybrid frequentist/Bayesian ranking statistic that makes use of the Bayesian evidence. We compute the Bayesian evidence under the assumption that the data either contain a coherent gravitational-wave signal, noise, or a glitch ($Z^S, Z^N, Z^G$, defined in Appendix~\ref{sec:bayesianEvidEval}). However, instead of computing true Bayesian odds, we use the evidences as a ranking statistic. We form a bootstrapped distribution of the evidence for simulated foreground and background events in order to form a frequentist ranking statistic.

@@

We acquire O2 candidate signal triggers (times when the detector's data has a signal-to-noise ratio above a predetermined threshold) for \bcr analysis from \pycbc~\cite{pycbc_code, pycbc_og0, pycbc_og1, pycbc_og2, pycbc_og3, pycbc_og4, pycbc_og5, pycbc_og6}.  Some of the triggers are associated with gravitational-wave events and candidates, while others are glitches. We also acquire background and simulated triggers from \pycbc to calculate \bgrdbcr and estimate values for $\{\hat{\pi}^S,\hat{\pi}^G\}$ (see Appendix~\ref{apdx:tuning-prior-odds} for details on the estimation process). The triggers are divided into two week time-frames because the detector's sensitivity does not stay constant throughout the eight-month-long observing period~\cite{pycbc_og4}.

\begin{table}[t]
\caption[BBH parameters correspond to duration $<454\ \text{ms}$]{\label{tab:parameters}Trigger-selection lab-frame parameter space (parameters correspond to signals with durations $<454 \ \text{ms}$ and $q\geq0.1$).}
\centering
\begin{tabular}{lrr}
\toprule
           & Minimum & Maximum\\
\midrule
Component Mass 1 [\msun] & 31.54 & 491.68\\
Component Mass 2 [\msun] & 1.32 & 121.01\\
Total Mass [\msun] & 56.93 & 496.72\\
Chirp Mass [\msun] & 8.00 & 174.56\\
Mass Ratio & 0.1 & 0.98\\
\end{tabular}
\end{table}

For our study, we filter \pycbc triggers to include only those in the parameter ranges presented in Table~\ref{tab:parameters}. This region focuses our analysis on binary black hole mergers with total masses above $\gtrsim55 \msun$, corresponding to binary systems with signal durations $<454 \ \text{ms}$ and $q\geq0.1$. The filtering process leaves us with $60,996$ background, $5,146$ simulated, and $25$ candidate signal triggers. We also include events and candidate events reported by \GWTC and the \IAS group in our list of candidate signal triggers.  A plot of the component mass space constrained by our trigger filter is presented in Fig.~\ref{fig:templateBank}.

\begin{figure*}[!ht]
{\centering \includegraphics[width=0.75\linewidth]{images/template_bank.png}
}
% time for chunk 14
% 1176955218, Apr 23, 2017, 4:00 UTC
% 1178294418, May 08, 2017, 16:00 UTC
\caption[ BCR search space.]{Component-mass boundaries for our trigger filter and parameter estimation prior. Our search is constrained to the parameter space enclosed by the gold-colored hatches, while our prior is constrained to the slightly larger parameter space enclosed by the teal-colored hatches. The purple region labeled ``IMBH'' is the parameter space where merger remnants may be IMBHs.}\label{fig:templateBank}
\end{figure*}

@@

Finally, with the \candbcr and \bgrdbcr for each time-frame of triggers, we calculate the candidate signal's \pastrobcr.

@@

We analyze the O2 candidates with $\totMlab > 55~\msun$ and report candidates with $\pastrobcr\geq0.3$ in Table~\ref{tab:results}. The $\hat{\pi}^S$ and $\hat{\pi}^G$ values utilized for each time-frame are reported in Appendix~\ref{apdx:alphabeta}.

Various search pipeline \pastro are not mathematically equivalent~\cite{Galaudage:2020:PhRvD}. Moreover, \pastro is not equivalent to \pastrobcr. However, by comparing a candidate's pipeline \pastro with its \pastrobcr, we can compare how significant each pipeline deems the candidate. For comparison, in Table~\ref{tab:results} we report \pastro values from \GWTC~\cite{GWTC1}, PyCBC OGC-2~\cite{pycbc_ogc_2}, PyCBC OGC-3~\cite{pycbc_ogc_2}, PyCBC `single-search'~\cite{pycbc_single_det}, IAS~\cite{IAS1, IAS2}, and \citet{bayesian_odds}'s analyses.

@@

\bibliography{high_mass_bib}

\end{document}
